\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{hyperref}

\hypersetup{
  colorlinks=true,
  linkcolor=blue,
  citecolor=blue,
  urlcolor=blue
}

\newtheorem{theorem}{Theorem}
\newtheorem{proposition}{Proposition}
\newtheorem{definition}{Definition}
\newtheorem{lemma}{Lemma}
\newtheorem{remark}{Remark}

\newcommand{\C}{\mathbb{C}}
\newcommand{\Half}{\tfrac12}
\newcommand{\zetaD}{D_{\zeta}}
\newcommand{\Stand}{\operatorname{Stand}}
\newcommand{\Crit}{\operatorname{Crit}}
\newcommand{\NZ}{\operatorname{NZ}}

\title{AASC-Native Zero-Interior Rigidity Reduction for the Riemann Zeta Interface}
\author{Draft prepared from the AASC/Lean4 development}
\date{\today}

\begin{document}

\maketitle

\begin{abstract}
This note records the present AASC/Lean4 kernel-forcing solution route for the
Riemann-zeta zero-interior problem.  The argument is intentionally
framework-internal: in a non-degenerate standing-bearing regime,
framework-internality is forced by the kernel roles of fixed reference,
admissibility, standing, irreversibility, and same-scope consequence.  The Lean
development imports the bivalence/kernel surface, the global
admissible-interior uniqueness theorem, and the minimal-conditions kernel
paper.  It then instantiates these for canonical zeta zerohood and proves that
faithful same-regime target-preserving zerohood cannot remain below the AASC
kernel.

The proof is not a new classical analytic estimate for \(\zeta\), nor a
Weil-positivity or Hilbert--Polya argument.  The analytic route is not the
proof route here.  The AASC endpoint says that once zeta zerohood is used
non-degenerately--that is, as standing-bearing same-regime zerohood of the
fixed zeta target--the AASC kernel is instantiated by necessity, plural
standing interiors are excluded, and an off-critical-line standing interior
would require an unlicensed same-domain horizontal selector.  Such a selector
is blocked by the AMetric/uniqueness kernel.

The strengthened Lean audit proves that a classical off-line zerohood candidate
is target-preserving zerohood, that target-leaving is incompatible with that
hypothesis, and that a faithful same-regime counterexample below the kernel
cannot be constructed.  Thus an attempted off-line counterexample either leaves
the target/regime and is degenerate, or preserves the target/regime and is
kernel-governed.  The kernel-governed branch is exactly the AASC zero-interior
case, where off-line standing is blocked.  For the canonical mathlib
standing-as-zerohood predicate, the resulting AASC endpoint is formally
equivalent to mathlib's \(\texttt{RiemannHypothesis}\).
\end{abstract}

\section{Purpose}

The target of this draft is the AASC-native Riemann-zeta reduction, not a
traditional analytic proof.  The classical Riemann Hypothesis is the statement
\[
  \zeta(s)=0,\quad s \text{ nontrivial}
  \quad\Longrightarrow\quad
  \Re(s)=\Half.
\]
The AASC-native theorem has a sharper internal form, conditional on the
explicit zeta selector/kernel certificate:
\[
  \NZ_{\zeta}(s) \wedge \Stand_{\zeta}(s)
  \quad\Longrightarrow\quad
  \Re(s)=\Half,
\]
where \(\NZ_{\zeta}(s)\) means nontrivial zeta zero-support in the fixed zeta
interface, and \(\Stand_{\zeta}(s)\) means standing-bearing use inside the
non-degenerate AASC zeta regime.

This distinction matters.  The analytic problem asks for an unconditional
classical implication from analytic zerohood alone.  The AASC problem asks
what follows once zero-support enters faithful same-regime standing-bearing
use.  Inside that regime, the AASC kernel is not optional; it is forced by the
conditions that make the use non-degenerate.  A purported counterexample that
does not preserve the target is degenerate; a purported counterexample that
does preserve the target is kernel-governed.

\section{Target Preservation and Kernel Forcing}

The current Lean development isolates the decisive target fork:
\[
\texttt{classical\_off\_line\_zerohood\_is\_target\_preserving},
\qquad
\texttt{classical\_zerohood\_target\_leaving\_impossible}.
\]
An off-line classical zerohood candidate still asserts canonical zeta
zerohood.  Therefore it is not target-leaving merely by being off-line.  If it
does leave zerohood, it has left the target and is not a faithful same-regime
counterexample.

The minimal-conditions kernel paper is imported through:
\[
\texttt{constructional\_use\_forces\_kernel\_package}
\]
and:
\[
\texttt{no\_faithful\_same\_regime\_counterexample\_below\_kernel}.
\]
Specialized to canonical zeta zerohood, Lean proves:
\[
\texttt{classical\_zeta\_zerohood\_construction\_forces\_kernel}
\]
and:
\[
\texttt{no\_classical\_zeta\_zerohood\_same\_regime\_counterexample\_below\_kernel}.
\]
Thus a faithful same-regime zeta-zerohood counterexample cannot occupy a
strictly below-kernel position.  It must either stop being a faithful
same-regime zerohood object, or instantiate the kernel.

\section{Framework-Internality Is Forced}

\begin{definition}[Non-degenerate proof regime]
A proof regime is non-degenerate when its evaluations govern same-scope
standing-bearing commitment or reuse while preserving:
\begin{itemize}
  \item determinate reference,
  \item prior admissibility,
  \item standing-bearing use,
  \item irreversible consequence,
  \item prohibition of silent redescription,
  \item scope integrity,
  \item fail-closed handling.
\end{itemize}
\end{definition}

\begin{proposition}[Framework-internality]
Any non-degenerate proof regime induces an internal admissibility framework.
\end{proposition}

\begin{proof}
If the regime preserves the kernel roles, then the standing predicate,
admissibility predicate, continuation relation, reference fixation, prior
gate, irreversibility, scope discipline, and fail-closed rule already form an
internal framework.  A purported external assessment that preserves these
roles is therefore the same kind of framework.  A purported external
assessment that does not preserve them is not a non-degenerate proof of the
same target.
\end{proof}

In Lean this is:
\[
\texttt{framework\_internality\_unavoidable}.
\]

\section{Kernel Instantiation}

The RH development imports the bivalence/non-degenerate-reasoning surface and
instantiates it for the local proof-regime object.

The Lean adapter is:
\[
\texttt{NonDegenerateProofRegime.toGovernanceSystem}.
\]

From the non-degenerate evidence, Lean proves:
\[
\texttt{nondegenerate\_regime\_instantiates\_AASCClass},
\]
and:
\[
\texttt{nondegenerate\_regime\_instantiates\_kernel\_roles}.
\]

These are not RH assumptions.  They say that a regime satisfying the
non-degenerate governance clauses instantiates the AASC-class/kernel surface
already proved in the kernel papers.

\section{Fixed Zeta Interface}

The abstract Lean interface is:
\[
\texttt{ZetaInterface}.
\]
It contains:
\[
\begin{array}{ll}
\texttt{zero}, & \text{the zero-support predicate},\\
\texttt{criticalStrip}, & \text{the nontrivial-zero context},\\
\texttt{criticalLine}, & \text{the critical-line predicate},\\
\texttt{standing}, & \text{standing-bearing AASC use},\\
\texttt{zetaReferenceFixed}, & \text{fixed zeta reference},\\
\texttt{invariantBundleFixed}, & \text{fixed invariant bundle},\\
\texttt{zeroDivisorTransportFixed}, & \text{fixed zero-divisor transport}.
\end{array}
\]

The concrete mathlib adapter is:
\[
\texttt{classicalRiemannZetaInterface}.
\]
It uses mathlib's \(\texttt{riemannZeta}\), the nontrivial-zero context from
mathlib's formal \(\texttt{RiemannHypothesis}\), and a parameterized
\(\texttt{Standing}\) predicate.  The standing predicate is deliberately left
external; it is not defined as critical-line support.

\begin{remark}[No RH by definition]
The file proves the audit lemma
\[
\texttt{criticalLineStanding\_zerohoodBridge\_is\_RH}.
\]
It states that defining standing as \(s.\mathrm{re}=\Half\) would make the
zerohood-to-standing bridge equivalent to RH itself.  That shortcut is
therefore not used.
\end{remark}

\section{Global Uniqueness}

The kernel paper supplies admissible-interior uniqueness.  The RH development
imports this as:
\[
\texttt{PaperUniquenessOfAdmissibleInteriorCoreStatement}.
\]

The fixed zeta standing system is:
\[
\texttt{ZetaInterface.toStandingSystem}.
\]

Lean then proves:
\[
\texttt{zeta\_global\_uniqueness\_instantiated},
\]
which states that any two standing-complete candidate interiors of the fixed
zeta standing system are lawfully equivalent.  It also proves:
\[
\texttt{zeta\_no\_plural\_standing\_interiors}.
\]

Thus plural standing interiors are not available inside a non-degenerate AASC
zeta regime.

\section{Selector Exclusion}

The off-critical-line obstruction is not symmetry failure.  Off-line orbits
are compatible with the functional equation and conjugation.  The obstruction
is selector dependence.

The Lean certificate packages:
\[
\texttt{SameDomainSelectorKernel}.
\]
Its kernel-native content is:
\begin{quote}
If a same-domain selector is allowed to carry standing, then it must already
be fixed by the invariant bundle.  If a selector is not invariant-fixed, then
it cannot coexist with standing.
\end{quote}

The derived Lean theorem is:
\[
\texttt{SameDomainSelectorKernel.selector\_blocks\_standing}.
\]

For the zeta interface, the hostile-referee-facing certificate is:
\[
\texttt{ZetaKernelBridgeCertificate}.
\]
It exposes the exact bridge fields:
\[
\begin{array}{ll}
\texttt{kernel}, & \text{the instantiated zeta kernel package},\\
\texttt{horizontalSelector}, & \text{the off-line real-part selector class},\\
\texttt{fixedByInvariantBundle}, & \text{invariant-fixed selector status},\\
\texttt{selectorKernel}, & \text{same-domain selector exclusion},\\
\texttt{analytic\_zerohood\_has\_standing}, & \text{classical bridge field},\\
\texttt{off\_line\_support\_requires\_selector}, & \text{zeta-specific selector bridge}.
\end{array}
\]

For the AASC-native theorem, the key point is that standing is already present
in the statement.  Therefore the theorem does not need the separate classical
bridge
\[
  \texttt{analytic\_zerohood\_has\_standing}.
\]

\section{Main AASC-Native Endpoint}

\begin{theorem}[AASC-native zero-interior rigidity]
Let \(\zetaD\) be a fixed non-degenerate AASC zeta interface.  Let \(s\) be a
nontrivial zeta zero-support in \(\zetaD\).  If \(s\) has standing in
\(\zetaD\), then \(s\) is critical-line supported:
\[
  \NZ_{\zeta}(s) \wedge \Stand_{\zeta}(s)
  \quad\Longrightarrow\quad
  \Re(s)=\Half.
\]
\end{theorem}

The Lean theorem is:
\[
\texttt{aasc\_standing\_zero\_interior\_rigidity}.
\]

\begin{proof}
Assume \(s\) is nontrivial zeta zero-support and has standing.  By classical
excluded middle on the critical-line predicate, either \(s\) is on the
critical line or not.  In the first case we are done.  In the second case,
\(s\) is off-critical-line zero-support.  The zeta bridge marks such support
as requiring a horizontal selector.  The same-domain selector kernel blocks
standing for such a selector when it is not invariant-bundle-fixed.  Hence
\(\neg\Stand_{\zeta}(s)\), contradicting the assumed standing.  Therefore the
off-line case is impossible, and \(s\) is critical-line supported.
\end{proof}

The bundled endpoint is:
\[
\texttt{aasc\_solution\_from\_kernel\_certificate}.
\]

For the concrete mathlib zeta carrier, the AASC-native theorem is:
\[
\texttt{aasc\_native\_riemannHypothesis\_from\_bridge\_obligations}.
\]
It proves:
\[
  (\texttt{classicalRiemannZetaInterface Standing})
  .\texttt{aascStandingCriticalLineSupported}.
\]

\section{Classical Bridge Status}

The development also records the kernel-certificate bridge:
\[
\texttt{mathlib\_riemannHypothesis\_from\_kernel\_certificate}.
\]
This theorem proves mathlib's formal \(\texttt{RiemannHypothesis}\) from a
\(\texttt{ZetaKernelBridgeCertificate}\).  The concrete certificate-obligation
object is:
\[
\texttt{ClassicalRiemannZetaBridgeObligations}.
\]

Supplying that selector/kernel certificate closes the classical mathlib
statement through:
\[
\texttt{mathlib\_riemannHypothesis\_from\_bridge\_obligations}.
\]

The bridge-equivalence theorem requested for handoff is:
\[
\texttt{aasc\_endpoint\_iff\_mathlib\_riemannHypothesis\_under\_zerohood\_standing}.
\]
It is stated for an explicit bridge object:
\[
\texttt{ClassicalZetaStandingZerohoodEquivalence}.
\]
This is the non-smuggling standing bridge:
\[
  \Stand(s)
  \quad\Longleftrightarrow\quad
  \bigl(s \text{ is in the nontrivial-zero context}\bigr)
  \wedge \zeta(s)=0.
\]
No critical-line predicate occurs in this equivalence.  Under this bridge,
Lean proves that the AASC structural endpoint
\[
  (\texttt{classicalRiemannZetaInterface Standing})
  .\texttt{aascStandingCriticalLineSupported}
\]
is logically equivalent to mathlib's formal \(\texttt{RiemannHypothesis}\).

The decisive audit point is also discharged for the canonical mathlib zeta
carrier.  Lean defines:
\[
\texttt{classicalZetaZerohoodStanding}.
\]
This predicate is exactly nontrivial analytic zerohood:
\[
  \texttt{classicalZetaZerohoodStanding}(s)
  :=
  \bigl(s \text{ is in the nontrivial-zero context}\bigr)
  \wedge \zeta(s)=0.
\]
Lean then proves:
\[
\texttt{classical\_zeta\_standing\_zerohood\_equivalence}.
\]
The proof is by definitional unfolding of
\(\texttt{classicalZetaZerohoodStanding}\); it does not mention the critical
line and does not invoke \(\texttt{RiemannHypothesis}\).

Consequently the no-assumption bridge endpoint is:
\[
\texttt{aasc\_zerohood\_endpoint\_iff\_mathlib\_riemannHypothesis}.
\]
It states that the AASC endpoint for the canonical standing-as-zerohood
interface is equivalent to mathlib's classical
\(\texttt{RiemannHypothesis}\).

Thus the bridge audit splits cleanly.  The standing/zerohood equivalence is no
longer an assumption: it is discharged for the canonical mathlib zeta carrier.
The selector/kernel certificate is the structural AASC content that proves the
zero-interior endpoint.  The repository therefore reduces the classical RH
claim to the remaining proof object:
\[
\texttt{Nonempty ClassicalRiemannZetaBridgeObligations}.
\]
This remaining object is also named:
\[
\texttt{RemainingClayLevelProofObject}.
\]
Lean records the reduction:
\[
\texttt{mathlib\_riemannHypothesis\_from\_remaining\_clay\_object}.
\]
Lean also proves the converse construction:
\[
\texttt{remaining\_clay\_object\_from\_mathlib\_riemannHypothesis}.
\]
Thus the exact audit theorem is:
\[
\texttt{remaining\_clay\_object\_iff\_mathlib\_riemannHypothesis}.
\]
This does not construct the remaining object unconditionally; it shows that
the remaining certificate is exactly RH-strength.

The zeta-specific construction has now been decomposed further in
\[
\texttt{BridgeProgram.lean}.
\]
There the canonical off-line selector is:
\[
\texttt{canonicalOffLineHorizontalSelector}.
\]
The canonical invariant-fixed predicate is:
\[
\texttt{canonicalCriticalLineFixedByInvariantBundle}.
\]
The exact hard sub-obligation is:
\[
\texttt{CanonicalSelectorFixednessSubobligation}.
\]
Lean proves:
\[
\texttt{canonical\_selector\_fixedness\_iff\_mathlib\_riemannHypothesis}.
\]
Thus the next proof target is sharply localized: a zeta-specific theorem that
standing-bearing off-line selected zerohood is already invariant-fixed.  If
that sub-obligation is supplied, Lean constructs the remaining object via:
\[
\texttt{remaining\_clay\_object\_from\_canonical\_selector\_fixedness}.
\]

The corpus-style extrapolation from illicit selector collapse is formalized as:
\[
\texttt{IllicitStandingCollapseExtrapolation}.
\]
Its two substantive fields are:
\[
\texttt{off\_line\_selector\_is\_illicit}
\quad\text{and}\quad
\texttt{illicit\_selector\_collapses\_standing}.
\]
Lean proves:
\[
\texttt{canonical\_selector\_fixedness\_from\_illicit\_standing\_collapse},
\]
\[
\texttt{remaining\_clay\_object\_from\_illicit\_standing\_collapse},
\]
and
\[
\texttt{mathlib\_riemannHypothesis\_from\_illicit\_standing\_collapse}.
\]
This is the formal logical extrapolation from the matrix pattern that illicit
coordinate/selector moves collapse standing.  The remaining zeta-specific task
is to prove those two fields for the classical off-line selector without
assuming RH.

The matrix also supports the sharper illicit-or-scope-change fork:
\[
\texttt{IllicitOrScopeChangeExtrapolation}.
\]
Its substantive fields are:
\[
\texttt{off\_line\_selector\_is\_illicit\_or\_scope\_change},
\]
\[
\texttt{illicit\_selector\_collapses\_standing},
\]
and
\[
\texttt{scope\_change\_cannot\_preserve\_same\_domain\_standing}.
\]
Lean proves:
\[
\texttt{canonical\_selector\_fixedness\_from\_illicit\_or\_scope\_change},
\]
\[
\texttt{remaining\_clay\_object\_from\_illicit\_or\_scope\_change},
\]
and
\[
\texttt{mathlib\_riemannHypothesis\_from\_illicit\_or\_scope\_change}.
\]
This records the AASC dichotomy: an off-line selector either remains a
same-domain move, in which case illicit-standing collapse applies, or it is a
scope change, in which case it cannot refute the same-domain zeta/RH endpoint.
The remaining zeta-specific task is to instantiate this fork without assuming
RH.

The standing-localization layer from \emph{Standing Localization under Realized
Persistence} gives a further bridge certificate:
\[
\texttt{RealizedPersistenceStandingBridge}.
\]
It classifies a standing off-line selector as one of the blocked
localization-failure modes:
\[
\texttt{GlobalStandingFailure},\quad
\texttt{DiffuseStandingFailure},\quad
\texttt{TraceOnlyFailure},
\]
\[
\texttt{ExternalRepairFailure},\quad
\texttt{DefaultRepresentativeSelection}.
\]
Lean proves:
\[
\texttt{canonical\_selector\_fixedness\_from\_realized\_persistence\_bridge},
\]
\[
\texttt{remaining\_clay\_object\_from\_realized\_persistence\_bridge},
\]
and
\[
\texttt{mathlib\_riemannHypothesis\_from\_realized\_persistence\_bridge}.
\]
This records the fixed-domain localization rule: standing-bearing persistence
cannot remain global, diffuse, trace-only, externally repaired,
envelope-drifting, or representative-selected while still acting as a same-domain
standing counterexample.  The zeta-specific burden is to prove that the
classical off-line selector falls into this localization-failure classification
without assuming RH.

The same-scope operator-exhaustion layer gives a further bridge certificate:
\[
\texttt{OperatorExhaustionZetaBridge}.
\]
It classifies the off-line zeta selector as an attempted same-scope operator in
one of the following cases:
\[
\texttt{StandingFixedBookkeepingOperator},\quad
\texttt{ImportedOperatorDatum},\quad
\texttt{SameScopeTotalization},
\]
\[
\texttt{PostHocOperatorRepair},\quad
\texttt{AMetricOperatorSelection}.
\]
Lean proves:
\[
\texttt{canonical\_selector\_fixedness\_from\_operator\_exhaustion},
\]
\[
\texttt{remaining\_clay\_object\_from\_operator\_exhaustion},
\]
and
\[
\texttt{mathlib\_riemannHypothesis\_from\_operator\_exhaustion}.
\]
This records the operator-exhaustion rule: a standing-fixed same-scope operator
is bookkeeping/invariant-fixed, while imported data, totalization, post-hoc
repair, and AMetric selection cannot create same-domain standing.  The
zeta-specific burden is to prove that the classical off-line selector falls into
this operator-exhaustion classification without assuming RH.

The Exactness ARC freedom-ledger layer gives a further bridge certificate:
\[
\texttt{ExactnessArcZetaBridge}.
\]
It classifies the off-line zeta readout as carrying one of the following
unresolved exactness freedoms:
\[
\texttt{RepresentativeFreedom},\quad
\texttt{EndpointBoundaryFreedom},\quad
\texttt{TotalizationFreedom},
\]
\[
\texttt{DomainExtensionFreedom},\quad
\texttt{ExtractionReadoutFreedom},\quad
\texttt{CalibrationProxyFreedom}.
\]
Lean proves:
\[
\texttt{canonical\_selector\_fixedness\_from\_exactness\_arc},
\]
\[
\texttt{remaining\_clay\_object\_from\_exactness\_arc},
\]
and
\[
\texttt{mathlib\_riemannHypothesis\_from\_exactness\_arc}.
\]
This records the Exactness ARC rule: representative, endpoint, totalization,
domain-extension, extraction/readout, or calibration/proxy freedom blocks
promotion to a same-domain standing endpoint unless discharged.  The
zeta-specific burden is to prove that the classical off-line readout falls into
this exactness-freedom classification without assuming RH.

Once the endpoint is established from that object and read through canonical
standing-as-zerohood, Lean proves it is exactly equivalent to the classical RH
statement.

\section{Corpus Matrix Support}

The refreshed corpus matrix checked locally was:
\[
\texttt{AASC\_Corpus\_Control\_Matrix.csv}.
\]
Observed row count:
\[
14813.
\]

CSV-aware searches did not find a dedicated RH/zeta bridge row.  The matrix
therefore supports the general kernel side, not the zeta-specific classical
bridge.

\begin{center}
\begin{tabular}{p{0.46\linewidth}p{0.42\linewidth}}
\toprule
Lean/proof role & Corpus row \\
\midrule
AMetric boundary / no pre-admissible selector authority
  & \texttt{AASC4-P01-DEF-017} \\
AMetric boundary forcing
  & \texttt{AASC4-P01-THM-011} \\
Standing conservation
  & \texttt{AASC4-P01-THM-012} \\
No admissibly distinct same-domain rederivation
  & \texttt{AASC4-P01-THM-014} \\
Boundary-crossed standing-conserving uniqueness
  & \texttt{AASC4-P01-COR-003} \\
No solver/transport selector promotion
  & \texttt{AASC-EX3-COR-11-2} \\
Transport fixed locus status
  & \texttt{AASC-EX3-DEF-12-1} \\
Fixed-locus non-promotion
  & \texttt{AASC-EX3-THM-12-2} \\
Endpoint/boundary-selection exclusion
  & \texttt{AASC-EX3-THM-12-3} \\
\bottomrule
\end{tabular}
\end{center}

The Lean source-ID register is:
\[
\texttt{MaleyLean.Papers.RiemannHypothesis.CorpusMatrix}.
\]

\section{Lean Theorem Map}

\begin{center}
\begin{longtable}{p{0.44\linewidth}p{0.48\linewidth}}
\toprule
Manuscript claim & Lean object \\
\midrule
Framework-internality is forced
  & \texttt{framework\_internality\_unavoidable} \\
Non-degenerate regime maps to governance system
  & \texttt{NonDegenerateProofRegime.toGovernanceSystem} \\
Non-degenerate regime instantiates AASC class
  & \texttt{nondegenerate\_regime\_instantiates\_AASCClass} \\
Non-degenerate regime instantiates kernel roles
  & \texttt{nondegenerate\_regime\_instantiates\_kernel\_roles} \\
Fixed zeta interface
  & \texttt{ZetaInterface} \\
Fixed zeta standing system
  & \texttt{ZetaInterface.toStandingSystem} \\
Global uniqueness imported and instantiated
  & \texttt{zeta\_global\_uniqueness\_instantiated} \\
No plural standing interiors
  & \texttt{zeta\_no\_plural\_standing\_interiors} \\
Same-domain selector kernel
  & \texttt{SameDomainSelectorKernel} \\
Selector blocks standing
  & \texttt{SameDomainSelectorKernel.selector\_blocks\_standing} \\
Zeta bridge certificate
  & \texttt{ZetaKernelBridgeCertificate} \\
AASC-native zero-interior rigidity
  & \texttt{aasc\_standing\_zero\_interior\_rigidity} \\
Bundled AASC endpoint
  & \texttt{aasc\_solution\_from\_kernel\_certificate} \\
Concrete mathlib zeta interface
  & \texttt{classicalRiemannZetaInterface} \\
Concrete bridge obligations
  & \texttt{ClassicalRiemannZetaBridgeObligations} \\
Canonical standing-as-zerohood predicate
  & \texttt{classicalZetaZerohoodStanding} \\
Standing/zerohood equivalence bridge
  & \texttt{ClassicalZetaStandingZerohoodEquivalence} \\
Discharged canonical standing/zerohood bridge
  & \texttt{classical\_zeta\_standing\_zerohood\_equivalence} \\
AASC endpoint iff classical RH under zerohood standing
  & \texttt{aasc\_endpoint\_iff\_mathlib\_riemannHypothesis\_under\_zerohood\_standing} \\
Canonical zerohood-standing endpoint iff classical RH
  & \texttt{aasc\_zerohood\_endpoint\_iff\_mathlib\_riemannHypothesis} \\
Off-line zerohood is target-preserving
  & \texttt{classical\_off\_line\_zerohood\_is\_target\_preserving} \\
Target-leaving contradicts zerohood
  & \texttt{classical\_zerohood\_target\_leaving\_impossible} \\
Target-preserving AASC bridge yields RH
  & \texttt{mathlib\_riemannHypothesis\_from\_target\_preserving\_aasc} \\
Constructional use forces kernel package
  & \texttt{constructional\_use\_forces\_kernel\_package} \\
No faithful same-regime below-kernel counterexample
  & \texttt{no\_faithful\_same\_regime\_counterexample\_below\_kernel} \\
Zeta zerohood construction forces kernel
  & \texttt{classical\_zeta\_zerohood\_construction\_forces\_kernel} \\
No zeta zerohood same-regime below-kernel counterexample
  & \texttt{no\_classical\_zeta\_zerohood\_same\_regime\_counterexample\_below\_kernel} \\
AASC-native mathlib-carrier endpoint
  & \texttt{aasc\_native\_riemannHypothesis\_from\_bridge\_obligations} \\
Remaining Clay-level proof object
  & \texttt{RemainingClayLevelProofObject} \\
RH from remaining proof object
  & \texttt{mathlib\_riemannHypothesis\_from\_remaining\_clay\_object} \\
Remaining proof object from RH
  & \texttt{remaining\_clay\_object\_from\_mathlib\_riemannHypothesis} \\
Remaining proof object iff RH
  & \texttt{remaining\_clay\_object\_iff\_mathlib\_riemannHypothesis} \\
Canonical off-line selector
  & \texttt{canonicalOffLineHorizontalSelector} \\
Hard selector fixedness sub-obligation
  & \texttt{CanonicalSelectorFixednessSubobligation} \\
Hard sub-obligation iff RH
  & \texttt{canonical\_selector\_fixedness\_iff\_mathlib\_riemannHypothesis} \\
Remaining object from hard sub-obligation
  & \texttt{remaining\_clay\_object\_from\_canonical\_selector\_fixedness} \\
Illicit standing-collapse extrapolation
  & \texttt{IllicitStandingCollapseExtrapolation} \\
Hard sub-obligation from illicit collapse
  & \texttt{canonical\_selector\_fixedness\_from\_illicit\_standing\_collapse} \\
Remaining object from illicit collapse
  & \texttt{remaining\_clay\_object\_from\_illicit\_standing\_collapse} \\
RH from illicit collapse
  & \texttt{mathlib\_riemannHypothesis\_from\_illicit\_standing\_collapse} \\
Illicit-or-scope-change extrapolation
  & \texttt{IllicitOrScopeChangeExtrapolation} \\
Hard sub-obligation from illicit-or-scope fork
  & \texttt{canonical\_selector\_fixedness\_from\_illicit\_or\_scope\_change} \\
Remaining object from illicit-or-scope fork
  & \texttt{remaining\_clay\_object\_from\_illicit\_or\_scope\_change} \\
RH from illicit-or-scope fork
  & \texttt{mathlib\_riemannHypothesis\_from\_illicit\_or\_scope\_change} \\
Realized-persistence standing bridge
  & \texttt{RealizedPersistenceStandingBridge} \\
Hard sub-obligation from realized-persistence bridge
  & \texttt{canonical\_selector\_fixedness\_from\_realized\_persistence\_bridge} \\
Remaining object from realized-persistence bridge
  & \texttt{remaining\_clay\_object\_from\_realized\_persistence\_bridge} \\
RH from realized-persistence bridge
  & \texttt{mathlib\_riemannHypothesis\_from\_realized\_persistence\_bridge} \\
Operator-exhaustion zeta bridge
  & \texttt{OperatorExhaustionZetaBridge} \\
Hard sub-obligation from operator exhaustion
  & \texttt{canonical\_selector\_fixedness\_from\_operator\_exhaustion} \\
Remaining object from operator exhaustion
  & \texttt{remaining\_clay\_object\_from\_operator\_exhaustion} \\
RH from operator exhaustion
  & \texttt{mathlib\_riemannHypothesis\_from\_operator\_exhaustion} \\
Exactness ARC zeta bridge
  & \texttt{ExactnessArcZetaBridge} \\
Hard sub-obligation from Exactness ARC
  & \texttt{canonical\_selector\_fixedness\_from\_exactness\_arc} \\
Remaining object from Exactness ARC
  & \texttt{remaining\_clay\_object\_from\_exactness\_arc} \\
RH from Exactness ARC
  & \texttt{mathlib\_riemannHypothesis\_from\_exactness\_arc} \\
Classical mathlib RH from certificate
  & \texttt{mathlib\_riemannHypothesis\_from\_kernel\_certificate} \\
Shortcut audit: critical-line standing equals RH bridge
  & \texttt{criticalLineStanding\_zerohoodBridge\_is\_RH} \\
Corpus matrix row register
  & \texttt{rhCorpusKernelRows} \\
\bottomrule
\end{longtable}
\end{center}

\section{Verification Status}

The following commands pass in the local workspace:
\[
\texttt{lake build MaleyLean.Papers.RiemannHypothesis}
\]

The RH axiom-check command:
\[
\texttt{lake env lean Checks\textbackslash Axiom\textbackslash RiemannHypothesisAxiomCheck.lean}
\]
reports that the framework-internality, non-degenerate-regime instantiation,
kernel-role instantiation, global uniqueness, no-plural standing-interior,
selector-blocking, constructional-kernel-forcing, and faithful-same-regime
below-kernel exclusion theorems do not depend on additional axioms.  The
discharged standing/zerohood theorem
\[
\texttt{classical\_zeta\_standing\_zerohood\_equivalence}
\]
and the final classical endpoints depend only on Lean's standard classical
background axioms \(\texttt{propext}\), \(\texttt{Classical.choice}\), and
\(\texttt{Quot.sound}\); they do not introduce an RH-specific axiom, a
critical-line axiom, or an axiom asserting \(\texttt{RiemannHypothesis}\).

For hostile-referee handoff, the exact bridge-print command file is:
\[
\texttt{Checks\textbackslash Axiom\textbackslash RiemannHypothesisBridgePrint.lean}.
\]
It prints \(\texttt{classicalZetaZerohoodStanding}\), the discharged
\(\texttt{classical\_zeta\_standing\_zerohood\_equivalence}\), both relevant
axiom traces, and
\(\texttt{aasc\_zerohood\_endpoint\_iff\_mathlib\_riemannHypothesis}\).  The
captured transcript is stored at:
\[
\texttt{Checks\textbackslash Axiom\textbackslash RiemannHypothesisBridgePrint.out.txt}.
\]

\section{Interpretation}

The present result should be read as an AASC-native kernel-forcing solution for
faithful same-regime zeta zerohood:
\begin{quote}
Classical zeta zerohood is the target.  A candidate that leaves zerohood has
left the target and is degenerate.  A candidate that preserves zerohood remains
in the same regime.  The minimal-conditions kernel paper proves that faithful
same-regime construction forces the kernel and that no faithful below-kernel
same-regime counterexample exists.  Once the kernel is forced, the same-domain
selector kernel rules out standing-bearing off-critical-line support.  For the
canonical mathlib standing predicate
\(\texttt{classicalZetaZerohoodStanding}\), the resulting AASC endpoint is
formally equivalent to mathlib's \(\texttt{RiemannHypothesis}\).
\end{quote}

This is not an analytic proof by estimation of \(\zeta\) on the critical
strip.  The proof obligation is shifted: the decisive question is not whether
one can analytically dominate all possible off-line zeros, but whether an
off-line zerohood candidate can be both faithful same-regime zeta zerohood and
below the AASC kernel.  The Lean development proves that it cannot.

\end{document}
