\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{array}
\usepackage{booktabs}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{remark}{Remark}

\newcommand{\AASC}{\mathrm{AASC}}
\newcommand{\UEAP}{\mathrm{UEAP}}
\newcommand{\MR}{\mathrm{MR}}
\newcommand{\NNR}{\mathrm{NNR}}
\newcommand{\GCI}{\mathrm{GCI}}
\newcommand{\SigmaLeg}{\Sigma\text{-}\mathrm{Leg}}

\title{Non-Degenerate UEAP Kernel Operationalization\\
for the Standing Neutrino Splitting-Ratio Branch Audit}
\author{Soma Maley}
\date{\today}

\begin{document}

\maketitle

\begin{abstract}
We give the branch-audit proof that the standing neutrino splitting-ratio
problem closes to a singleton once the target is treated as a non-degenerate
same-scope regime. The central observation is that the UEAP claim-standing
audit is not an additional empirical or discretionary filter. In a
non-degenerate regime it is the admissibility kernel operationalized: every
surviving branch must make a UEAP sigma-legitimate claim, while every
non-current branch is forced by the kernel to fail one UEAP legitimacy
coordinate. The current branch is point-identifying by unique admissible
interior occupancy. Hence all non-current branches are eliminated and the
hybrid joint restriction has the current standing ratio as its unique
survivor. The proof is mapped to the accompanying Lean formalization in
\texttt{MaleyLean/Papers/Neutrino/RatioBlocker.lean}.
\end{abstract}

\section{Purpose}

This note records the paper-facing proof corresponding to the Lean object
\[
\texttt{AASCNondegenerateUEAPKernelOperationalization C M H N S}.
\]
The result is a bridge from the non-degenerate admissibility kernel to the
UEAP branch audit for the standing neutrino splitting-ratio problem. In the
Lean development, inhabiting this object is sufficient to derive
\[
\texttt{nondegenerateUEAPKernelOperationalizationGiveJointSingleton}
\]
and
\[
\texttt{nondegenerateUEAPKernelOperationalizationRulesOutSecondPoint}.
\]

The proof should be read as a closure audit. It does not compute a numerical
mass or import observed splitting values. It establishes that, under the
admitted AASC same-scope restrictions, every non-current route fails
claim-standing, while the current route is uniquely point-identifying.

\section{Lean4 Provenance and Theorem Map}

The Lean4 formalization provenance status used in this note is:
\[
\text{Lean4 build status reported.}
\]
The local repository command
\[
\texttt{lake build MaleyLean.Papers.Neutrino}
\]
completed successfully on 2026-05-28. This is a reported local build status
for the repository formalization. Independent build audit of a manuscript
submission package remains a verification task, not a manuscript premise.

The word ``current'' in ``current standing ratio'' means current within the
admitted AASC standing ledger. It does not mean the current empirical best-fit
ratio or an imported numerical experimental value.

\begin{center}
\small
\begin{tabular}{>{\raggedright\arraybackslash}p{0.34\linewidth}
                >{\raggedright\arraybackslash}p{0.56\linewidth}}
\toprule
Manuscript claim or dependency & Lean object or theorem \\
\midrule
Standing ratio certificate \(C\) &
\texttt{StandingRatioCertificate};
\texttt{StandingRatioCertificateAdmitted};
\texttt{standingRatioCertificateAdmitted}. \\
\addlinespace
MR3 spectral-source admission \(M\) &
\texttt{MR3SpectralSourceAdmission};
\texttt{MR3SpectralSourceAdmissionWitness};
\texttt{MR3CorpusTheorems.admitsSource}. \\
\addlinespace
Hybrid modular/spectral/scoto restriction \(H\) &
\texttt{AASCHybridCompressionNetwork};
\texttt{AASCHybridSameScopeAdmissionWitness};
\texttt{hybridSameScopeAdmissionWitnessClearsH}. \\
\addlinespace
No-eleventh-route census \(N\) &
\texttt{AASCNoEleventhNeutrinoRoute};
\texttt{AASCNoEleventhRouteCensusWitness};
\texttt{noEleventhRouteCensusWitnessClearsN}. \\
\addlinespace
Corpus support ledger \(S\) &
\texttt{AASCCorpusBranchSupportLedger};
\texttt{corpusSupportLedgerAdmitted}. \\
\addlinespace
Non-degenerate kernel admission &
\texttt{AASCNondegenerateKernelInteriorAdmission};
\texttt{nondegenerateKernelAdmissionFromCurrentPointIdentification}. \\
\addlinespace
Branch impossibility audit &
\texttt{AASCBranchImpossibilityAudit};
\texttt{branchImpossibilityAuditAsConcreteBranchFailureTable}. \\
\addlinespace
Admissible ratio branch singleton locked &
\texttt{HybridJointRestrictionSingleton};
\texttt{branchAuditAndKernelAdmissionWitnessesGiveEndpointSingleton}. \\
\addlinespace
No second admissible branch &
\texttt{HybridJointRestrictionHasSecondPoint};
\texttt{branchAuditAndKernelAdmissionWitnessesRuleOutSecondPoint}. \\
\bottomrule
\end{tabular}
\end{center}

\section{Standing Neutrino Ratio Setting}

Let \(C\) be the standing neutrino splitting-ratio certificate. It contains
two non-collapsed response roles, the solar and atmospheric splitting roles,
together with a common carrier, a fixed atmospheric denominator, a subordinate
solar-to-atmospheric relation, and the reportable standing ratio. Let \(M\)
be the MR3 spectral-source admission, let \(H\) be the hybrid
modular/spectral/scoto compression network, let \(N\) be the no-eleventh-route
census, and let \(S\) be the corpus support ledger.

The hybrid joint restriction is the class of ratios \(r\) such that
\[
 r \in C.\mathrm{inMinimalInterval},\qquad
 H_{\mathrm{mod}}(r),\qquad
 H_{\mathrm{spectral}}(r),\qquad
 H_{\mathrm{scoto}}(r).
\]
The no-eleventh-route census assigns every exposed route carrier a finite
draft branch index. The current branch is
\[
\texttt{currentStandingRatio}.
\]
Here ``current'' is ledger-current: the branch selected by the admitted AASC
standing certificate and its route census, not a numerical experimental
best-fit value.
The non-current branches are:
\[
\begin{array}{ll}
\texttt{modularOnlyBranch}, &
\texttt{scotoParameterFiberBranch},\\
\texttt{spectralWithoutFiniteCollapseBranch}, &
\texttt{sterileScopeExtensionBranch},\\
\texttt{phaseTopologyBreakingBranch}, &
\texttt{matterTransportBreakingBranch},\\
\texttt{absoluteMassImportBranch}, &
\texttt{diracMajoranaSelectorBranch},\\
\texttt{identitySelectorBranch}. &
\end{array}
\]

\section{UEAP as Kernel Operationalized}

\begin{definition}[UEAP kernel operationalization]
In a non-degenerate AASC regime, UEAP is the operational form of the
admissibility kernel when expressed as a claim-standing audit. A branch that
survives the hybrid joint restriction must satisfy UEAP sigma-legitimacy for
its exposed branch class. A non-current branch fails exactly when the kernel
forces failure of at least one UEAP legitimacy coordinate.
\end{definition}

This definition is important because it prevents UEAP from being treated as
an extra optional screen. The non-degenerate kernel already determines which
same-scope claims are admissible. UEAP merely records those kernel conditions
as auditable coordinates: target fixation, carrier adequacy, fixed meaning,
fixed scope, target-carrier alignment, exhaustion modulo skin, laundering
exclusion, ancestry separation, boundary declaration, evidence-network
closure, and report preservation.

\section{Current Branch}

\begin{lemma}[Current-class point identification]
In the non-degenerate standing regime, any hybrid-joint ratio whose route
carrier has current draft class is extensionally the current standing ratio.
\end{lemma}

\begin{proof}
The non-degenerate kernel applies because the target is not a degenerate
placeholder, empty boundary object, pure notation choice, or free parameter
fiber. It is a standing same-target object over two non-collapsed response
roles with fixed denominator, fixed carrier, and fixed role relation.

By the kernel and unique-interior results, non-degenerate standing occupies
the unique admissible interior. Thus two same-domain current-class occupants
cannot remain distinct unless they introduce a new admissibility-bearing role,
boundary, or carrier distinction. Those possibilities are excluded by the
same-scope residual admission and quotient-skin discipline. Therefore the
current-class occupant is the current standing ratio.

In Lean this is the point-identification content of
\[
\texttt{AASCNondegenerateKernelInteriorAdmission}.
\]
\end{proof}

\section{Non-Current Branch Audit}

\begin{lemma}[Joint survivors must be UEAP-legitimate]
If a branch survives the hybrid joint restriction, then its exposed draft
class must satisfy UEAP sigma-legitimacy.
\end{lemma}

\begin{proof}
A surviving branch is not merely compatible evidence or a suggestive model
fragment. It purports to close the same standing target under the admitted
hybrid restriction. Therefore it is a claim-standing route. Since UEAP is the
kernel operationalized, any such route must satisfy the UEAP sigma-legitimacy
conditions for its draft class.
\end{proof}

\begin{lemma}[Kernel-forced coordinate failures]
Each non-current draft branch has a kernel-forced UEAP coordinate failure.
\end{lemma}

\begin{proof}
The branch-by-branch assignments are shown in Table~\ref{tab:branch-audit}.
Each row records one way in which the non-current branch fails to satisfy the
claim-standing coordinates required by the non-degenerate admissibility
kernel.
\end{proof}

\begin{table}[htbp]
\centering
\small
\begin{tabular}{>{\raggedright\arraybackslash}p{0.24\linewidth}
                >{\raggedright\arraybackslash}p{0.25\linewidth}
                >{\raggedright\arraybackslash}p{0.39\linewidth}}
\toprule
Branch & UEAP coordinate failure & Corpus reason \\
\midrule
\texttt{modularOnlyBranch} &
\texttt{alternativesNotExhaustedModuloSkin} &
NNR4G/H magnitude-compression blocks promotion from modular motif, texture,
or carrier polynomial to the target ratio unless all same-scope alternatives
are exhausted modulo skin. \\
\addlinespace
\texttt{scotoParameterFiberBranch} &
\texttt{launderingNotExcluded} &
Residual-parameter and scoto/seesaw audits block hidden parameter repair. A
live parameter fiber cannot be laundered into first-principles closure unless
source-fixed, quotient-skin, or forced by the shared locus. \\
\addlinespace
\texttt{spectralWithoutFiniteCollapseBranch} &
\texttt{evidenceNetworkNotClosed} &
Fixed-domain exhaustion and quotient-fiber exactness require finite collapse,
overlap, or quotient-fiber exhaustion before a spectral quotient can report
exact selection. \\
\addlinespace
\texttt{sterileScopeExtensionBranch} &
\texttt{scopeUnfixed} &
Sterile/gauge-singlet or AdS/transport extensions change the comparison scope
unless they project back through the admitted same-scope residual quotient. \\
\addlinespace
\texttt{phaseTopologyBreakingBranch} &
\texttt{reportNotPreserving} &
Oscillation phase topology gives coherent readback and compatibility, not an
independent magnitude selector for the splitting-ratio target. \\
\addlinespace
\texttt{matterTransportBreakingBranch} &
\texttt{targetCarrierMisaligned} &
Matter-effect or transport behavior is a compatibility discriminator. Moving
the ratio requires an operator strengthening not conservative on the fixed
base, hence target-carrier misalignment. \\
\addlinespace
\texttt{absoluteMassImportBranch} &
\texttt{boundaryNotDeclared} &
Absolute mass, beta-decay, or cosmological information is boundary data for a
different measurement family and cannot be promoted as an undeclared
splitting-ratio selector. \\
\addlinespace
\texttt{diracMajoranaSelectorBranch} &
\texttt{targetAncestryNotSeparated} &
Dirac/Majorana status may constrain models, but as a ratio selector it
introduces endpoint or identity ancestry not separated from the target
derivation. \\
\addlinespace
\texttt{identitySelectorBranch} &
\texttt{carrierInadequate} &
Identity, normalization, chart, or representation choices are quotient skin or
bookkeeping unless they alter standing-bearing content; as selectors they lack
an adequate carrier. \\
\bottomrule
\end{tabular}
\caption{UEAP coordinate failures assigned to non-current neutrino draft
branches.}
\label{tab:branch-audit}
\end{table}

\section{Main Closure Theorem}

\begin{theorem}[Non-degenerate UEAP branch closure]
In the admitted non-degenerate same-scope neutrino regime, the hybrid joint
restriction has no non-current survivor. Its unique survivor is the current
standing ratio.
\end{theorem}

\begin{proof}
Let \(r\) be a ratio in the hybrid joint restriction. If the route carrier of
\(r\) has the current draft class, then by current-class point identification
\(r\) is the current standing ratio.

Suppose instead that the route carrier of \(r\) has a non-current draft class.
Since \(r\) survives the hybrid joint restriction, the branch must claim UEAP
sigma-legitimacy. But by Table~\ref{tab:branch-audit}, and by the fact that
UEAP is the kernel operationalized in a non-degenerate regime, the same branch
has a kernel-forced UEAP coordinate failure. A coordinate failure is a UEAP
legitimacy blocker, and a legitimacy blocker excludes sigma-legitimacy.
Contradiction.

Thus no non-current branch survives. The only possible survivor is the
current branch, and the current branch is point-identifying. Therefore the
hybrid joint restriction is a singleton with value \(C.\mathrm{ratio}\).
\end{proof}

\begin{corollary}[No second point]
There is no second point in the hybrid joint restriction.
\end{corollary}

\begin{proof}
Immediate from the singleton theorem.
\end{proof}

\section{Formalization Map}

The paper proof corresponds to the following Lean declarations:
\[
\begin{array}{ll}
\text{Kernel admission} &
\texttt{AASCNondegenerateKernelInteriorAdmission},\\
\text{UEAP operationalization} &
\texttt{AASCNondegenerateUEAPKernelOperationalization},\\
\text{Coordinate ledger} &
\texttt{AASCUEAPCitedCoordinateBranchLedger},\\
\text{Branch audit} &
\texttt{AASCBranchImpossibilityAudit},\\
\text{Singleton theorem} &
\texttt{nondegenerateUEAPKernelOperationalizationGiveJointSingleton},\\
\text{No-second-point theorem} &
\texttt{nondegenerateUEAPKernelOperationalizationRulesOutSecondPoint}.
\end{array}
\]

The logical path in Lean is:
\[
\begin{aligned}
&\texttt{AASCNondegenerateUEAPKernelOperationalization}\\
&\quad\Longrightarrow
\texttt{AASCUEAPCitedCoordinateBranchLedger}\\
&\quad\Longrightarrow
\texttt{AASCUEAPCoordinateBranchRegistry}\\
&\quad\Longrightarrow
\texttt{AASCUEAPBranchAudit}\\
&\quad\Longrightarrow
\texttt{AASCBranchImpossibilityAudit}\\
&\quad\Longrightarrow
\texttt{HybridJointRestrictionSingleton}.
\end{aligned}
\]

\section{Corpus Handles}

The proof appeals to the following source families.

\begin{itemize}[leftmargin=2em]
\item \emph{Claim Standing and Legitimacy}: UEAP legitimacy, blockers, and
sigma-legitimacy exclusion.
\item Kernel and unique-interior papers, including \emph{Unus Solus
Possibilis Est}: non-degenerate kernel necessity and unique admissible
interior occupancy.
\item The Impossibility Suite and \emph{Septem Sigilla Necessitatis}: no
partial closure and no hidden repair.
\item Fixed-domain exhaustion, AMetric Boundary, and Closure by Exhaustion:
quotient-fiber discipline and exhaustion closure.
\item Fixed-Base Operator Constraints, Collapse of Operator-Level
Strengthening, and Invariant Selection and Endpoint Structure: operator and
endpoint selector discipline.
\item Role-Occupancy Closure under Admissibility: no same-role splitting
without a new admissible role.
\item ATS and equivalence-exhaustion results: skin/bookkeeping separation.
\end{itemize}

\section{Conclusion}

The standing neutrino splitting-ratio closure is obtained by treating the
target as a non-degenerate same-scope AASC regime. In that regime, the UEAP
audit is forced by the admissibility kernel. Every non-current branch fails a
kernel-forced UEAP coordinate, while any branch surviving the hybrid joint
restriction would have to be UEAP sigma-legitimate. This contradiction removes
all non-current branches. The current branch is point-identifying by unique
admissible interior occupancy. Therefore the hybrid joint restriction closes
to the current standing ratio as a singleton.

\end{document}
